Demo arXiv template

### 2022-10-24 paper/paper.qmd
a draft on tidy data- need more work

@@

TODO: see if there is any paper describing this type of pains

@@

TODO: useful to reference tidy data and tidy model that makes the workflow on modelling tidy somewhere in introduction

@@

@@

TODO: first sentence: tailor to their indices without thinking about the big picture

@@

Before the concept of tidy data [@wickham_tidy_2014], tabular data arrive at data analysts in all different ways. 
Different analysts would write customised scripts for analysing the specific data. 
These scripts can be extended to other data analysed by the same people or group but this is not generalizable directly to another dataset. 
When the tidy data concept comes, variables and values are arranged so that 1) Each variable forms a column, 2) Each observation forms a row, and; 3) Each type of observational unit forms a table.
With this specific layout, wrangling on tabular data can be standardised into a grammar of data manipulation in `dplyr` [@dplyr].

A similar issue happens with index construction where researchers construct their own indices in their own ways and there has not yet been a tidy principle on index construction.
Also, this tidy principle on index construction is more complex than those in tidy data and the `dplyr` package.
It has to encompass the workflow of transformation from the raw data towards the final index series.

>>>>

*see if there is any paper describing this type of pains*

*useful to reference tidy data and tidy model that makes the workflow on modelling tidy somewhere in introduction*

@@

@@

@@

*first sentence: tailor to their indices without thinking about the big picture*

@@

@@

As a programming language for data analysis, R provides a scripted environment for users to experiment with data without the complex abstraction a typical programming language requires. 
The flexible and intuitive workflow is paramount for data analysis since in a data analysis project, the full workflow of how data should be processed from the raw data to the final results is usually only consolidated till the end of the project and analysts need the freedom to quickly experiment with different ideas when working with data.
This approach to data analysis is enhanced by the tidyverse suite where a collection of R packages are built for data science under the concept of tidy data. 
The tidy data principle [@wickham_tidy_2014] prescribes three simple rules for structuring tabular data: 1) Each variable forms a column, 2) Each observation forms a row, and; 3) Each type of observational unit forms a table.
The packages built in the tidyverse suite provide operations that are direct actions on the data and users, even new users, can easily read from the code on what has been performed and what to expect after each operation. 
Researchers and analysts have a similar need for an intuitive and flexible process to construct indices since a similar workflow occurs where researchers experiment with many different indices, discover issues with the current ones, and experiment with potential ideas before finally arrive at a solution.

<!-- Researchers working on index construction should consider adopt a workflow where operations on data can be clearly reflected by the code while flexible to experiment  -->

<!-- Before the concept of tidy data [@wickham_tidy_2014], tabular data arrive at data analysts in all different ways.  -->
<!-- Different analysts would write customised scripts for analysing the specific data.  -->
<!-- These scripts can be extended to other data analysed by the same people or group but this is not generalizable directly to another dataset.  -->
<!-- When the tidy data concept comes, variables and values are arranged so that 1) Each variable forms a column, 2) Each observation forms a row, and; 3) Each type of observational unit forms a table. -->
<!-- With this specific layout, wrangling on tabular data can be standardised into a grammar of data manipulation in `dplyr` [@dplyr].  -->

<!-- A similar issue happens with index construction where researchers construct their own indices in their own ways and there has not yet been a tidy principle on index construction. -->
<!-- Also, this tidy principle on index construction is more complex than those in tidy data and the `dplyr` package. -->
<!-- It has to encompass the workflow of transformation from the raw data towards the final index series. -->

### 2022-10-24 paper/paper.tex
a draft on tidy data- need more work

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, frame hidden, sharp corners, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

@@

TODO: see if there is any paper describing this type of pains

TODO: useful to reference tidy data and tidy model that makes the
workflow on modelling tidy somewhere in introduction

@@

@@

Before the concept of tidy data (Wickham 2014), tabular data arrive at
data analysts in all different ways. Different analysts would write
customised scripts for analysing the specific data. These scripts can be
extended to other data analysed by the same people or group but this is
not generalizable directly to another dataset. When the tidy data
concept comes, variables and values are arranged so that 1) Each
variable forms a column, 2) Each observation forms a row, and; 3) Each
type of observational unit forms a table. With this specific layout,
wrangling on tabular data can be standardised into a grammar of data
manipulation in \texttt{dplyr} (Wickham et al. 2022).

A similar issue happens with index construction where researchers
construct their own indices in their own ways and there has not yet been
a tidy principle on index construction. Also, this tidy principle on
index construction is more complex than those in tidy data and the
\texttt{dplyr} package. It has to encompass the workflow of
transformation from the raw data towards the final index series.

@@

\leavevmode\vadjust pre{\hypertarget{ref-dplyr}{}}%
Wickham, Hadley, Romain François, Lionel Henry, and Kirill Müller. 2022.
\emph{Dplyr: A Grammar of Data Manipulation}.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

\emph{see if there is any paper describing this type of pains}

\emph{useful to reference tidy data and tidy model that makes the
workflow on modelling tidy somewhere in introduction}

@@

@@

\emph{first sentence: tailor to their indices without thinking about the
big picture}

@@

As a programming language for data analysis, R provides a scripted
environment for users to experiment with data without the complex
abstraction a typical programming language requires. The flexible and
intuitive workflow is paramount for data analysis since in a data
analysis project, the full workflow of how data should be processed from
the raw data to the final results is usually only consolidated till the
end of the project and analysts need the freedom to quickly experiment
with different ideas when working with data. This approach to data
analysis is enhanced by the tidyverse suite where a collection of R
packages are built for data science under the concept of tidy data. The
tidy data principle (Wickham 2014) prescribes three simple rules for
structuring tabular data: 1) Each variable forms a column, 2) Each
observation forms a row, and; 3) Each type of observational unit forms a
table. The packages built in the tidyverse suite provide operations that
are direct actions on the data and users, even new users, can easily
read from the code on what has been performed and what to expect after
each operation. Researchers and analysts have a similar need for an
intuitive and flexible process to construct indices since a similar
workflow occurs where researchers experiment with many different
indices, discover issues with the current ones, and experiment with
potential ideas before finally arrive at a solution.

@@
